### 2023-12-24 sections/3-datasets.tex
changes to datasets section
some restructuing of datasets and results

In addition to benchmarks on datasets from the ANN Benchmarks suite, we also benchmarked on synthetic augmentations of these real datasets, using the process described in \ref{subsec:methods:synthetic-data}. In particular, we use a noise tolerance $\epsilon = 0.01$ and explore the scaling behavior as the multiplier $m$ of new points increases. While we explored the scaling behavior of CAKES with augmented versions of each dataset in \ref{table:datasets:summary}, we give an in-depth discussion in \ref{sec:results} of results for scaling behavior on fashion-mnist, glove-100, gist, and a purely random dataset.

@@

\subsection{Silva}
\label{subsec:silva}

Add section about Silva.

\subsection{Radio ML}
The RadioML dataset contains samples of both live and synthetically generated signal captures of different modulation modes over a range of SNR levels. Specifically, it is comprised of 24 modulation modes at 26 different SNR levels ranging from -20 dB to 30 dB, with 4,096 samples at each modulation mode and SNR level~\cite{oshea2018radioml}. Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total. Each sample provided in RadioML can be thought of as an array of 2048 floating point values for a single signal capture with labels for SNR and modulation mode.

>>>>

@@

\subsection{Random Datasets and Synthetic Augmentations}
\label{subsec:random-datasets}

In addition to benchmarks on datasets from the ANN Benchmarks suite, we also benchmarked on synthetic augmentations of these real datasets, using the process described in \ref{subsec:methods:synthetic-data}. 
In particular, we use a noise tolerance $\epsilon = 0.01$ and explore the scaling behavior as the cardinality multiplier (refered to as ``scale'' in Table~\ref{table:results:ann-fashion} {\color{red} TODO: merge the tables into one and confirm this reference is still correct after the merge}) increases.

We also benchmarked on a purely random dataset with the same cardinality and dimensionality as sift: 1,000,000 points in 128 dimensions. 
This benchmark allows us to isolate the effect of a manifold structure (which we expect to be absent in a purely random dataset) on the performance of CAKES's algorithms.

\subsection{Silva}
\label{subsec:silva}
Silva 18S~\cite{10.1093/nar/gks1219} contains ribosomal DNA sequences of approximately 2.25 million genomes with an aligned length of 50,000 letters.
We use Levenshtein distance with this dataset.
% I think this needs another sentence but I'm not sure what else to say

\subsection{Radio ML}
The RadioML dataset contains samples of both live and synthetically generated signal captures of different modulation modes over a range of SNR levels. 
Specifically, it is comprised of 24 modulation modes at 26 different SNR levels ranging from -20 dB to 30 dB, with 4,096 samples at each modulation mode and SNR level~\cite{oshea2018radioml}. 
Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total. 
Each sample provided in RadioML can be thought of as an array of 2048 floating point values for a single signal capture with labels for SNR and modulation mode.
We use Dynamic Time Warping distance with this dataset.
